\chapter*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments} % add contents line for Acknowledgments

My time in graduate school has been a singular experience - I both cannot imagine going through it again, and also cherish this time above any other in my life so far. During this time I have experience both the lowest of lows, but have also made some of my closest friends and accomplished more than I dreamed myself capable of. I could not have completed this journey without the support and friendship of a legion of people, a few of whom I would like to explicitly thank here.

I would be remiss not to start with my advisor, Bart. I arrived here with a blank slate as an astronomy researcher, but you gave me a chance and a reason to continue with graduate school. Thank you for your patience, expert guidance, and most of all for giving me the space and time to screw up a lot. I could not have asked for a better mentor and advisor.

None of this would even have been possible without my wonderful parents. Thank you for a lifetime of love and support. You have always been there for me no matter what, and without judgement or criticism.

I thankfully recognized early on the importance of grad school peers, which was a major reason for my coming to Wisconsin. I came here for a slip of paper and a head full of star-stuff, and I leave with a heart full of friends. I would definitely have not made it through classes and prelims alone without my amazing and talented classmates, Emily, Erin, and Alisha.

An extra special thank you to Emily for being the best office mate ever - putting up with my many grumpy days, and always being ready for a solid complaining session over happy hour cocktails. 

Ben T., thanks for always being a friend and confidant, and for the laughs, jams, and soggy-bottomed canoes. You always inspire me with your work ethic and care for details. I'll miss having you just a block and a department floor away. 

Arthur, you are the epitome of elite professionalism, a totally righteous dude, and I count myself lucky to call you a close friend. I hope I never stop being amazed and enlightened by your oddball, open-hearted worldview. 

Ben R., I share your cantankerous take on many levels, and I'm glad to have had you around this last year. Perhaps distance just makes the heart grow fonder, but I would probably be willing to attend a Phish concert with you sometime. Remember not to get too caught up in all the malarkey, you're too legit of a dude for it to matter.

Thank you to all The Begowatts - Aaron, Arthur, Ben, Chris, Dan, Lydia, Robert, and Tom for helping me live out my rock star dreams. Man we started at the bottom, but dang it if we didn't make ourselves into a respectable rock 'n' roll outfit by the end! Aaron - keep it burning for little Aaron Jr, I've already been missing your giraffe-rock stance and rain-poncho-chic style (and don't be afraid to occasionally turn the bass down). Arthur - your willingness to indulge the unknown was instrumental for this band. I hope you get out there and keep playing, you're a great, creative drummer (but watch the tempo)! Ben - I really hope you keep playing also, you're the finest guitarist I've had the pleasure of playing with. Your rock-steady approach will always be underrated. Chris - the world needs your vocal harmonies. Dan - never stop learning new styles, techniques, and don't be afraid to reinvent yourself (and easy on the cymbals). I'll miss your rock-steady bashing behind me. Lydia - your music taste is second to none; it's time for DJ Voldemort to rise again. Robert and Tom - you guys completely revitalized this band and I can't express how much I'm going to miss rocking with you. 

And finally, to my partner in crime, Claire. In so many ways I would literally not be here without you. Thank you for continually inspiring me to be a better writer, scientist, and person (and for putting up with my chronic slowness and bad jokes). We have been continuously warned about this ``two-body problem", but we have beaten it into submission every step of the way. It is no match for the two of us. I can't wait to embark on our next adventure together. 